---
title: "CaseStudy_DDS"
author: "Tahir Ahmad, Alec Neff,"
date: "6/27/2018"
output: html_document
---

---
title: "CaseStudy_DDS"
author: "Tahir Ahmad"
date: "June 21, 2018"
output:
    html_document:
        keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## INTRODUCTION
This is Case Study on Beers and Breweries. There are two datasets in this study: Beers and Breweries. The Beers dataset contains a list of 2410 US craft beers and Breweries dataset contains 558 US breweries. In this study the following questions are answered:
1) The number of breweries are present in each state
2) New data set is presented called beers_n_breweries. This new dataset is the merging of dataset Beers and Breweries.
3) The number of NA's in each column
4) Computing the median alcohol content and international bitterness unit for each state. 
5) State that has the maximum alcoholic (ABV) beer. State that has the most bitter (IBU) beer.
6) Summary statistics for the ABV variable
7) To report if there is an apparent relationship between the bitterness of the beer and its alcoholic content

## Reading the csv files

```{r read_csv}
breweries <- read.csv("https://raw.githubusercontent.com/tikisen/6306-case-study-1/master/Breweries.csv", quote = "", row.names = NULL, stringsAsFactors = FALSE, header = TRUE)
beers <- read.csv("https://raw.githubusercontent.com/tikisen/6306-case-study-1/master/Beers.csv", quote = "", row.names = NULL, stringsAsFactors = FALSE, header = TRUE)
```
## Question 1: The number of breweries present in each state

```{r breweries_state}
library(plyr)
breweries_state <- count(breweries$State)
colnames(breweries_state) <- c("State", "Number of Breweries")
breweries_state
```

## Question 2: Merging of Datasets
New data set is presented called beers_n_breweries. This new dataset is the merging of dataset Beers and Breweries.
```{r merging}
colnames(beers)[5] <- "Brew_ID"
beers2 <- merge.data.frame(beers, breweries, by = "Brew_ID")
colnames(beers2)[2] <- "Beers Name"
colnames(beers2)[8] <- "Breweries Name"
#Print the first 6 observation
head(beers2,6)
#Print the last 6 observation
tail(beers2,6)
```
  
# 3
### Report the number of NA's in each column.  
```{r,echo=TRUE}
colSums(is.na(beers2))
```

# 4
### Compute the median alcohol content and international bitterness unit for each state.  Plot a bar chart to compare.  
```{r, echo=TRUE}
abv<-na.omit(beers2$ABV)
ibu<-na.omit(beers2$IBU)
median(abv)
median(ibu)
hist(abv)
hist(ibu)
```
