---
title: "Case Study 1"
author: "Alec Neff"
date: "6/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r,echo=FALSE}
beers<-read.csv(file = "/Users/acneff/Documents/Data_Science/School/DDS/CaseStudy1/Beers.csv")
breweries<-read.csv(file = "/Users/acneff/Documents/Data_Science/School/DDS/CaseStudy1/Breweries.csv")
```
# Questions

## 1
How many breweries are present in each state?
  
```{r,echo=TRUE}
table(breweries$State)
```

## 2
Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.  
```{r,echo=TRUE}
bnb<-merge(beers,breweries,by.x = "Brewery_id",by.y = "Brew_ID")
bnb<-bnb[-1]
colnames(bnb)[colnames(bnb)=="Name.x"]<-"Beer"
colnames(bnb)[colnames(bnb)=="Name.y"]<-"Brewery"
head(bnb)
tail(bnb)
```

# 3
### Report the number of NA's in each column.  
```{r,echo=TRUE}
colSums(is.na(bnb))
```

# 4
### Compute the median alcohol content and international bitterness unit for each state.  Plot a bar chart to compare.  
```{r, echo=TRUE}
abv<-na.omit(bnb$ABV)
ibu<-na.omit(bnb$IBU)
median(abv)
median(ibu)
hist(abv)
hist(ibu)
```

## 5
Which state has the maximum alcoholic (ABV) beer?  Which state has the bitterest (IBU) beer?  
```{r,echo=TRUE}
bnb[which.max(bnb$ABV),]
bnb[which.max(bnb$IBU),]
```

## 6
Summary statistics for the ABV variable.  
```{r,echo=TRUE}
summary(abv)
```

## 7
Is there an apparent relationship between the bitterness of the beer and its alcoholic content?  Draw a scatter plot.  
```{r,echo=TRUE}
plot(bnb$ABV,bnb$IBU,main = "Plot of ABV vs IBU",xlab = "ABV",ylab = "IBU")
```
  
*It would appear that there is a slight correlation in beers less bitter than an IBU of 80.  The lack of an obvious overall trend is, in my opinion, a result of the bitter taste of hops added most famously to IPA-style beers, the fact that alcohol has less of a taste, per se, than a signiture oral sensation (fumyness and warmth), and the existence of relatively sweet ciders with ABVs rivaling a doppelbock's.*