---
title: "Farrow_Case_Study"
author: "Richard Farrow"
date: "6/24/2018"
output: html_document
---

```{r Data_Initialization, echo=TRUE}
library(RCurl)
beers <- getURL('https://raw.githubusercontent.com/tikisen/6306-case-study-1/master/Beers.csv')
ds_beers <- read.csv(textConnection(beers),header=TRUE)
head(ds_beers)

breweries <- getURL('https://raw.githubusercontent.com/tikisen/6306-case-study-1/master/Breweries.csv')
ds_breweries <- read.csv(textConnection(breweries),header=TRUE)
head(ds_breweries)
```

1. How many breweries are present in each state?
```{r Question_1, echo=TRUE}
library(plyr)
breweries.state <- count(ds_breweries$State)
colnames(breweries.state) <- c("State","Total Breweries")
breweries.state
```

2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.
```{r Question_2, echo=TRUE}
head(ds_beers)
head(ds_breweries)

colnames(ds_breweries)[1] <- "Brewery_id"
colnames(ds_breweries)[2] <- "Brewery_Name"
colnames(ds_beers)[1] <- "Beer_Name"

ds_combined <- merge(ds_beers,ds_breweries,by=c("Brewery_id","Brewery_id"))
head(ds_combined,6)
tail(ds_combined,6)
```

3. Report the number of NA's in each column.
```{r Question_3, echo=TRUE}
sapply(ds_combined,function(x) sum(is.na(x)))
```

4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.
```{r Question_4, echo=TRUE}
median_abv <- tapply(ds_combined$ABV,ds_combined$State,median)
barplot(median_abv)
median_ibu <- tapply(ds_combined$IBU,ds_combined$State,median)
barplot(median_ibu)
```

5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?
```{r Question_5, echo=TRUE}
max_abv <- tapply(ds_combined$ABV,ds_combined$State,max)
df <- as.data.frame(max_abv)
max(df,na.rm=TRUE)
abv_idx <- which(df$max_abv == max(df,na.rm=TRUE))
for (i in 1:length(abv_idx)){
  print(df[abv_idx[i],])
}

max_ibu <- tapply(ds_combined$IBU,ds_combined$State,max)
df <- as.data.frame(max_ibu)
max(df,na.rm=TRUE)
ibu_idx <- which(df$max_ibu == max(df,na.rm=TRUE))
for (i in 1:length(ibu_idx)){
  print(df[ibu_idx[i],])
}
```

6. Summary statistics for the ABV variable.
```{r Question_6, echo=TRUE}
summary(max_abv)
```

7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.
```{r Question_6, echo=TRUE}
plot(ds_combined$ABV,ds_combined$IBU)
plot(max_abv,max_ibu)
```


